Appendix S1. Linear regression models and non-linear population dynamics

### 2024-05-02 Appendix_S1_v01.Rmd
trying to update

>>>>

# One species, logistic growth, environmental covariate
We now consider using a linear model to analyze population growth when the species growth rate is impacted by a single environmental covariate.

## Growth depends on environment

First we add environment-dependent growth rate. The growth rate $r_i$ becomes:

$$ r_i = \hat{W}e^{-(E-x_{i,t})^2}$$

Here, $\hat{W}$ is the maximal population growth rate (set to )

equation becomes:

$$ N_{i,t+1} = \frac{r_i N_{i,t}}{1 + \alpha_{ii} N_{i,t}}$$

We make this not linked to then linked to growth and in each instance run a linear model to show no effect is detected or is detected as it should be. E can vary randomly, as long as it links to growth.

```{r}
# Simulate initial species population growth
N1.0 <- rpois(1,10)
r1.0 <- 1.67
alpha.11 <- 0.00125
# model function
disc_log <- function(r, N0, alpha) {
    Nt1 <- (r*N0) / (1+alpha*N0)
    return(Nt1)
}
# Simulation of model for t time steps
t <- 30
N <- rep(NA, t)
N[1] <- N1.0
for (i in 2:t) {
  N[i] <- disc_log(r=r1.0, N0=N[i-1], alpha=alpha.11)
}
```
